
While it is often possible to find exact MPO representation to represent a wide class of hamiltonians \todo{find citation and examples}, it is much harder to do the same for exponentiated operators. These operators play an important role: they act as time evolution operators for quantum systems $ \ket{\Psi(t)} = \exp( -i \hat{H} t ) \ket{\Psi(0)}$. A very similar operator governs the partition function in statistical mechanics: the probability of finding a system at inverse temperature $\beta = \frac{1}{T}$ in a microstate i is given by $p_i\exp{ - \beta \hat{H_i} }$. This is often called "imaginary" time, due to the substitution $\beta = i t$. \todo{explain link CFT}. The ability to calculate these operators is essential for understanding the dynamics of a given quantum model, and making contact with real world obsevations of these systems at finite temperature.

\subsection{Statistical mechanics}

The physics of a system in thermodynamical equilibrium can be derived from it's partition function Z. The classical formula generalises to a density matrix $\rho$ as follows:
\begin{equation}
  \begin{split}
    Z &= \sum e^{ - \beta E_n} \\
    &= \sum_n \Braket{n | e^{ - \beta \hat{H} }  | n} \\
    &= \Tr( e^{ - \beta \hat{H} } )
  \end{split}
\end{equation}
The first line is the partition function for clasical discrete systems. The index n runs of all possible microstates. It is known that the propability to find the system in a given microstates is given by:
\begin{equation}
  p_i = \frac{\sum e^{ - \beta E_i}}{Z}
\end{equation}
An useful quantity is the density matrix $\rho$.
\begin{equation}
  \begin{split}
    \rho &= \sum_j p_i  \Ket{ \Psi_j} \Bra{\Psi_j}   \\
    &= \sum_j \frac{ e^{ - \beta \hat{H} } }{Z}  \Ket{ \Psi_j} \Bra{\Psi_j}
  \end{split}
\end{equation}
Whith this notation, the partition function Z and ensemble average of an operator $\hat{X}$ are given by:
\begin{equation}
  \begin{split}
    Z &= \Tr( \rho) \\
    \Braket{X} &= \Tr(\rho \hat{X})
  \end{split}
\end{equation}

\subsection{Time evolutions}
In quantum field theory, \todo{LSZ theorema herbekijken}, calculation of n-point correlation functions is extremely important to understand a given field theory.

\subsubsection{ground state}
One practical way of finding the ground state is cooling an intitial stata down very small T.

\subsection{Tensor network methods}
In the following section I will give a very short review of the current tensor network methods to simulate real or imaginary time evolution. This overview is mainly based on the review paper \cite{Paeckel2019}.

% https://arxiv.org/pdf/1901.05824.pdf

\subsubsection{Approximations to  \texorpdfstring{$ \hat{U}(\delta)$}{U}   }
The goal is to approximately make a MPO for a small timestep $\delta$ which gives a new MPS at time $t+\delta$.
\paragraph{TEBD}
Time-evolving block decimation (TEBD)  uses the Trotter-Suzuki decomposition. Suppose the chain is split in even and odd sites.
\begin{equation}
  \hat{H} = \hat{H}_{\text{even}}+\hat{H}_{\text{even}}
\end{equation}

\begin{equation}
  \begin{split}
    \hat{U} = e^{-i \delta \hat{H}_{\text{even}}}  e^{-i \delta \hat{H}_{\text{even}} }e^{-i \delta \left[ \hat{H}_{\text{even}}, \hat{H}_{\text{odd}} \right] }\\
    \approx e^{-i \delta \hat{H}_{\text{even}}}  e^{-i \delta \hat{H}_{\text{even}} }
  \end{split}
\end{equation}
This is now easy to solve: first apply $e^{-i \delta \hat{H}_{\text{even}}}$ for every even bond and aftwards  $e^{-i \delta \hat{H}_{\text{odd}}}$. The error is $O(\delta^2)$ and the number of steps to reach temperature $\beta$ is $\beta / \delta$. The error can be made small. This can be generalized to higher order schemes.

\paragraph{ MPO $W^{I,II}$}
These method directly use the MPO representation of a certain hamiltonian
\todo{MPO w1 and 2}
%https://tensornetwork.org/mps/algorithms/timeevo/
This is a more recent method (2015) to construct an MPO first detailed in \cite{Zaletel2015}. The idea is to generalise
\begin{equation}
  1+ \delta \sum_x H_x \rightarrow \prod_x (1+  \delta H_x)
\end{equation}
The error is formally still $O(\delta^2)$, but includes many more terms. The advantages lays in the fact that the form above has an efficient representation as an MPO. MPO $W^I$ and $W^II$ are capeble of dealing with long-ranged interaction terms which makes it suitable to simulate 2D systems \cref{Paeckel2019}

\subsubsection{global Krylov method }

Krylov methods are widely used in linear algebra to calculate eigenvectors. An example is the Lanczos algorithm. These methods are applied to MPS's, but do not fully make use of its structure. For this method, only a MPO representation is needed.

\todo{expand on this}

\subsubsection{MPS-local methods }

\paragraph{local Krylov}
The krylov methods from previous pragraph can be adapted to work on a reduced basis.

\paragraph{TDVP} Time-dependent variational principle (TDVP) can be seen as a further developement of the local krylov method.

Its also been formulated in as a tangent space algorithm, similar to the VUMPS derivation (\cref{vumps_Deriv}).
\begin{equation}
  i \frac{\partial \ket{ \Psi( A ) }}{\partial t} = \mathcal{P_{ A( t )} } H  \ket{ \Psi( A ) }
\end{equation}
Where the richt hand side is projected on the tanget space, because the left hand side is a also a tangent vector. (See \cite{Vanderstraeten2019}).
